Hippocampal segmentation with MAGeT

### 2012-10-17 paper.tex
reorg as a knitr project

\documentclass{article}
\usepackage[margin=1.5in]{geometry}
\usepackage{algorithm}
\usepackage{color}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{url}

@@

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

<<a2a, cache=TRUE, fig = T, echo = F, dev='CairoPDF', warning=F, error=F>>=
library(ggplot2)
multiplot <- function(..., plotlist=NULL, cols) {
    require(grid)

    # Make a list from the ... arguments and plotlist
    plots <- c(list(...), plotlist)

    numPlots = length(plots)

    # Make the panel
    plotCols = cols                          # Number of columns of plots
    plotRows = ceiling(numPlots/plotCols) # Number of rows needed, calculated from # of cols

    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(plotRows, plotCols)))
    vplayout <- function(x, y)
        viewport(layout.pos.row = x, layout.pos.col = y)

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
        curRow = ceiling(i/plotCols)
        curCol = (i-1) %% plotCols + 1
        print(plots[[i]], vp = vplayout(curRow, curCol ))
    }

#####################################################
# TRACC
t_naive      = read.csv(file='data/a2a_tracc_naive.csv')
t_data       = read.csv(file='data/a2a_tracc_results_2012_08_30.csv')
t_maj        = subset(t_data, method == 'majvote')
t_xcorr      = subset(t_data, method == 'xcorr')
t_nmi        = subset(t_data, method == 'nmi')
t_mean_naive = mean(t_naive$k)
t_ylimits    = c(0.7,0.85)

t_multiatlas = read.csv(file='data/a2a_tracc_multiatlas_2012_08_14.csv')
t_ma_means   = aggregate( k ~ num_atlases , data=t_multiatlas, mean)
t_maj$k_minus_ma_mean   <- t_maj$k   - t_ma_means[ t_maj$num_atlases - 3, 2 ]
t_xcorr$k_minus_ma_mean <- t_xcorr$k - t_ma_means[ t_xcorr$num_atlases - 3, 2 ]
t_nmi$k_minus_ma_mean   <- t_nmi$k   - t_ma_means[ t_nmi$num_atlases - 3, 2 ]

# Majority Vote
# plots kappa by numbeer of templates used
#geom = c('smooth'), line=1.5, formula=y~poly(x,2), method='lm') + 
t_maj_plot <- qplot(x=num_templates, y=k, data=t_maj, colour=as.factor(num_atlases), 
  geom = c('smooth')) + 
geom_hline(aes(yintercept=t_mean_naive)) + 
geom_hline(aes(yintercept = k, colour = as.factor(num_atlases)), linetype="dotted", 
  data = t_ma_means ) + 
opts(title = "ANIMAL\nMajority vote") +
opts(legend.position = "None") + 
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" ) + 
coord_cartesian(ylim=t_ylimits)

# X-Corr results with a full suite of templates
# plots kappa by top N templates choosen 
t_xcorr_plot <- qplot(x=top_n, y=k, data=t_xcorr,
colour=as.factor(num_atlases), geom=c('smooth')) + 
geom_hline(aes(yintercept=t_mean_naive))  +
coord_cartesian(ylim=t_ylimits) + 
opts(title = "X-Corr vote") +
opts(legend.position = "None") + 
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" ) + 
coord_cartesian(ylim=t_ylimits)

# NMI results with a full suite of templates
# plots kappa by top N templates choosen 
t_nmi_plot <- qplot(x=top_n, y=k, data=t_nmi,
colour=as.factor(num_atlases), geom=c('smooth')) +
geom_hline(aes(yintercept=t_mean_naive))  +
opts(title = "NMI vote") + 
opts(legend.position = "None") + 
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" ) + 
coord_cartesian(ylim=t_ylimits)

#####################################################
# ANTS

a_naive      = read.csv(file='data/a2a_ants_naive_2012_08_30.csv')
a_data       = read.csv(file='data/a2a_ants_results_2012_08_30.csv')
a_maj        = subset(a_data, method == 'majvote')
a_xcorr      = subset(a_data, method == 'xcorr')
a_nmi        = subset(a_data, method == 'nmi')
a_mean_naive = mean(a_naive$k)
a_ylimits    = c(0.7,0.85)

a_multiatlas = read.csv(file='data/a2a_ants_multiatlas_2012_08_14.csv')
a_ma_means   = aggregate( k ~ num_atlases , data=a_multiatlas, mean)
a_maj$k_minus_ma_mean   <- a_maj$k - a_ma_means[ a_maj$num_atlases - 3, 2 ]
a_xcorr$k_minus_ma_mean <- a_xcorr$k - a_ma_means[ a_xcorr$num_atlases - 3, 2 ]
a_nmi$k_minus_ma_mean   <- a_nmi$k   - a_ma_means[ a_nmi$num_atlases - 3, 2 ]

# Majority Vote
# plots kappa by numbeer of templates used

a_maj_plot <- qplot(x=num_templates, y=k, data=a_maj, colour=as.factor(num_atlases), 
  geom=c('smooth')) + 
geom_hline(aes(yintercept=a_mean_naive))  +
coord_cartesian(ylim=a_ylimits) + 
geom_hline(aes(yintercept = k, colour = as.factor(num_atlases)), linetype="dotted", 
  data = a_ma_means ) +
opts(title = "ANTS\nMajority vote")  +
opts(legend.position = "None") + 
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" )

# X-Corr results with a full suite of templates
# plots kappa by top N templates choosen 
a_xcorr_plot <- qplot(x=top_n, y=k, data=a_xcorr,
colour=as.factor(num_atlases), geom=c('smooth')) + 
geom_hline(aes(yintercept=a_mean_naive))  +
opts(title = "X-Corr vote") +
opts(legend.direction = "horizontal") + 
opts(legend.position = "bottom") + 
coord_cartesian(ylim=a_ylimits)  +
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" )

# NMI results with a full suite of templates
# plots kappa by top N templates choosen 
a_nmi_plot <- qplot(x=top_n, y=k, data=a_nmi,
colour=as.factor(num_atlases), geom=c('smooth')) +
geom_hline(aes(yintercept=a_mean_naive))  +
opts(title = "NMI vote") + 
opts(legend.position = "None") + 
coord_cartesian(ylim=a_ylimits) +
scale_colour_hue(name="Atlases") +
xlab( "Number of Templates" ) + 
ylab( "Kappa" )

#loess.control(trace.hat = c("approximate"), statistics = c("approximate"), surface = c("interpolate"))
pdf("a2a_kbytemplates.pdf", width=15, height=15)
multiplot(t_maj_plot  , a_maj_plot  ,
          t_xcorr_plot, a_xcorr_plot, 
          t_nmi_plot  , a_nmi_plot  , cols=2)
dev.off()

############################################
#  Kappa adjusted by Multi-atlas mean 
a_ylimits    = c(-0.03,0.04)
t_ylimits    = a_ylimits

t_maj_plot <- qplot(x=num_templates, y=k_minus_ma_mean, data=t_maj, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "ANIMAL\nMajority vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=t_ylimits)

t_xcorr_plot <- qplot(x=top_n, y=k_minus_ma_mean, data=t_xcorr, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "X-Corr vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=t_ylimits)

t_nmi_plot <- qplot(x=top_n, y=k_minus_ma_mean, data=t_nmi, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "NMI vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=t_ylimits)

a_maj_plot <- qplot(x=num_templates, y=k_minus_ma_mean, data=a_maj, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "ANTS\nMajority vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=a_ylimits)

a_xcorr_plot <- qplot(x=top_n, y=k_minus_ma_mean, data=a_xcorr, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "X-Corr vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=a_ylimits)

a_nmi_plot <- qplot(x=top_n, y=k_minus_ma_mean, data=a_nmi, colour=as.factor(num_atlases), geom = c('smooth'), se=FALSE) + 
opts(title = "NMI vote") + opts(legend.position = "None") + 
xlab( "Number of Templates" ) + ylab( "Kappa - MA means" ) + 
coord_cartesian(ylim=a_ylimits)

#print(a_nmi_plot)
#pdf("a2a_kminusMAmean.pdf", width=15, height=15)
multiplot(t_maj_plot  , a_maj_plot  ,
          t_xcorr_plot, a_xcorr_plot, 
          t_nmi_plot  , a_nmi_plot  , cols=2)
#dev.off()
@

@@

<<ADNI-baseline-volumes-prep,echo=F,cache=T>>=
data = read.csv('data/ADNI_baseline_volumes.csv')
unscaled=subset(data,Scaled==0 & Baseline==1 & DX != '')
attach(unscaled)
totals = data.frame(LONIUID,L+R,UCSFFSL_L+UCSFSL_R,MAPER_L+MAPER_R,UCSFSNT_L + UCSFSNT_R,SNT_L + SNT_R,DX)
colnames(totals) <- c("ID","MAGeT","FSL","MAPER","UCSFSNT","SNT","DX")
@

\begin{figure}[h]
<<ADNI-baseline-volumes-boxplot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes-prep',cache=T>>=
library(reshape2)
qplot(DX,value,data=melt(totals,id.vars=c("ID","DX"),measure.vars=c("FSL","MAPER","MAGeT","SNT"),na.rm=T),colour=variable,geom="boxplot")
@
  \caption{Comparison of HC volumes by FreeSurfer (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-boxplot}
\end{figure}

\begin{figure}[h]
<<ADNI-baseline-volumes-plot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes',cache=T>>=
library(reshape2)
qplot(SNT,value,data=melt(totals,id.vars=c("ID","SNT"),measure.vars=c("FSL","MAPER","MAGeT")),colour=variable, geom="smooth", method="lm")
@
  \caption{Comparison of HC volumes by FreeSurfer (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-plot}
\end{figure}

>>>>

\documentclass{article}\usepackage{graphicx, color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
\newcommand{\hlslot}[1]{\textit{#1}}%
\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage[margin=1.5in]{geometry}
\usepackage{algorithm}
\usepackage{color}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{url}

@@

\begin{document}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}\begin{verbatim}
## pdf 
##   2
\end{verbatim}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}

{\ttfamily\noindent\itshape\textcolor{messagecolor}{\#\# geom\_smooth: method="auto" and size of largest group is >=1000, so using gam with formula: y \textasciitilde{} s(x, bs = "cs"). Use 'method = x' to change the smoothing method.}}\end{kframe}\includegraphics[width=\maxwidth]{figure/a2a} 
\end{knitrout}

@@

\begin{figure}[h]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/ADNI-baseline-volumes-boxplot}

\end{knitrout}

  \caption{Comparison of HC volumes by FreeSurfer (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-boxplot}
\end{figure}

\begin{figure}[h]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\textcolor{warningcolor}{\#\# Warning: Removed 359 rows containing missing values (stat\_smooth).}}

{\ttfamily\noindent\textcolor{warningcolor}{\#\# Warning: Removed 355 rows containing missing values (stat\_smooth).}}

{\ttfamily\noindent\textcolor{warningcolor}{\#\# Warning: Removed 355 rows containing missing values (stat\_smooth).}}\end{kframe}

{\centering \includegraphics[width=\maxwidth]{figure/ADNI-baseline-volumes-plot}

\end{knitrout}

  \caption{Comparison of HC volumes by FreeSurfer (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-plot}
\end{figure}
